Democratizing Secure Two-Party Computation

### 2017-10-17 OaklandSubmission/ex.tex
intro related

\section{Motivating example}
\label{sec:ex}
%$w^Tx>0$, mnist logistic regression
Consider a  cloud service provider Bob that wants to provide a service to diagnose
whether a patient has breast cancer or not. Bob trains a machine learning classification model
that results in a vector $w$ (say of length 30) and a scalar $b$.
This model is the intellectual property of Bob and he  wants to keep it secret.
Given a patient's medical report, in the form of a vector $x$ (also of length 30),
the classifer predicts that the patient has breast cancer if $w^Tx>b$.
However, for this task Bob needs access to $x$, which is private data of a customer.

@@

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates (the cost of  conversion overweighs the gains of performing an arithmetic addition instead of a boolean addition). 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends.
\nc{I like the above point. Perhaps we can mention something like this earlier in the intro itself?}

The \tool compiler provides strong static guarantees. For example, a well typed
\tool program is guaranteed to execute to termination without errors. A \tool program cannot go into non-termination or dereference illegal memory, i.e., no buffer overflows or underflows can happen at run time. These guarantees are
much stronger than what are offered by production compilers such as {\tt gcc}.
The primary reason that we are able to achieve these guarantees is because
\tool has been designed to be verifiable and is backed by formal semantics. 
Furthermore, the compiler output is guaranteed to be a cryptographically secure
implementation of the functionality declared by the \tool code. 
Moreover, the \tool compiler also generates a C implementation that can be run natively on a single machine for functional testing.

>>>>

\section{Motivating example}
\label{sec:ex}
%$w^Tx>0$, mnist logistic regression
\divya{add reference to before and later... as mentioned we would run evaluations on secure prediction of different models. Here we describe scenario in detail..}

Consider a  cloud service provider Bob that wants to provide a service to diagnose
whether a patient has breast cancer or not. Bob trains a machine learning classification model
that results in a vector $w$ (say of length 30) and a scalar $b$.
This model is the intellectual property of Bob and he  wants to keep it secret.
Given a patient's medical report, in the form of a vector $x$ (also of length 30),
the classifer predicts that the patient has breast cancer if $w^Tx>b$.
However, for this task Bob needs access to $x$, which is private data of a customer.

@@

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates (the cost of  conversion overweighs the gains of performing an arithmetic addition instead of a boolean addition). 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends.

The \tool compiler provides strong static guarantees. For example, a well typed
\tool program is guaranteed to execute to termination without errors. A \tool program cannot go into non-termination or dereference illegal memory, i.e., no buffer overflows or underflows can happen at run time. Production compilers such as {\tt gcc} provide no such guarantees
for the code in Figure~\ref{fig:ex-aby}.
The primary reason that we are able to achieve these guarantees is because
\tool has been designed to be verifiable and is backed by formal semantics. 
Furthermore, the compiler output is guaranteed to be a cryptographically secure
implementation of the functionality declared by the \tool code. 
Moreover, the \tool compiler also generates a C implementation that can be run natively on a single machine for functional testing.

### 2017-10-17 OaklandSubmission/intro.tex

In this work, we develop and implement our framework \tool \nc{I still
  like EasyPC :)} \divya{I agree that \tool is bad. What would be the
  full form for EasyPC? Shouldn't it be EasySC?} for secure
computation that achieves generality, performance and programmer
productivity. The programmer writes a high level \divya{C-like}
program (instead of a circuit) to describe the function to be
computed. Our compiler automatically generates an SMC protocol using a
mix of Arithmetic and Boolean compute. Our compiler is general and can
work with any secure implementation of a mix of arithmetic and boolean
computations. In our work, we focus on semi-honest secure two-party
computation. We build on ABY \cite{aby} that provides the suitable
cryptographic back-end in this setting. We provide a formal type
system and prove correctness and security of our compiler. We evaluate
our system on various benchmarks such as logistic regression and
convolutional neural network (CNN) for MNIST data \cite{minionn},
naive bayes, decision trees from \cite{shafindss}. Evaluations show
that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). Below, we will  give an overview of \tool and
describe our contributions in more detail.

>>>>

In this work, we develop and implement our framework \tool\footnote{\tool, read as ``easy peasy'', stands for Easy 2 Party Computation} for secure
computation that achieves generality, performance and programmer
productivity. The programmer writes a high level \divya{C-like}
program (instead of a circuit) to describe the function to be
computed. Our compiler automatically generates an SMC protocol using a
mix of Arithmetic and Boolean compute. Our compiler is general and can
work with any secure implementation of a mix of arithmetic and boolean
computations. In our work, we focus on semi-honest secure two-party
computation. We build on ABY \cite{aby} that provides the suitable
cryptographic back-end in this setting. We provide a formal type
system and prove correctness and security of our compiler. We evaluate
our system on various benchmarks such as logistic regression and
convolutional neural network (CNN) for MNIST data \cite{minionn},
naive bayes, decision trees from \cite{shafindss}. Evaluations show
that protocols generated by our compiler match
the performance or outperform hand-crafted protocols in most cases (see
\sectionref{eval}). Below, we will  give an overview of \tool and
describe our contributions in more detail.
